Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-06-27 manuscript/draftcssa19.tex
Reword macroeconomics models.

The original model drew its inspiration from historical sociology, in Katz's influential study of middle of 19th century Hamilton, Canada~\cite{katz2013people}. Retaining this original motivation, we draw additional inspiration from economic sociology, in the work of Granovetter~\cite{granovetter2005}; urban sociology, in the work of Sampson~\cite{sampson2002} and others; and in anthropology, in the work on cooperation in small to medium scale societies~\cite{avner1994,white2011kinship}. The geographic and economic scale of the systems, the nature of social actors and time period of interest are all very different from the ones used to develop macroeconomic representative agent models~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification. Elaborating on the interplay of conceptual and methodological ideas among these disciplines is beyond the scope of this article. Instead, we anchor this work in economic sociology and revisit the insights from the above disciplines in the article's concluding section.

>>>>

The original model drew its inspiration from historical sociology, in Katz's influential study of middle of 19th century Hamilton, Canada~\cite{katz2013people}. Retaining this original motivation, we draw additional inspiration from economic sociology, in the work of Granovetter~\cite{granovetter2005}; urban sociology, in the work of Sampson~\cite{sampson2002} and others; and in anthropology, in the work on cooperation in small to medium scale societies~\cite{avner1994,white2011kinship}. The geographic and economic scale of the systems, the nature of social actors and time period of interest are all very different from the ones used to develop models of representative agents in macroeconomics~\cite{benhabib2018}, making the similarity between macroeconomic wealth dynamics models and our models not comparable without further justification. Elaborating on the interplay of conceptual and methodological ideas among these disciplines is beyond the scope of this article. Instead, we anchor this work in economic sociology and revisit the insights from the above disciplines in the article's concluding section.
